Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-10-05 ms.tex
Incorporating shane's edits up to Comparison with Monte Carlo section

The location of the spectral peak of the distribution is
\be \label{eq:tau_peak_scaling}
x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
\ee
The solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$. For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$. Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=4.6$. Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp} {\sim} 10^5$. At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core and improve for larger $\tau_0$ where the spectral peak is well outside of the line core.

>>>>

The location of the spectral peak of the distribution is
\be \label{eq:tau_peak_scaling}
x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
\ee
Hence, the solution of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$. For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$. Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=4.6$. Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp} {\sim} 10^5$. At fixed temperature, solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower $\tau_0$ where the peak of the spectrum lies near the core, but will improve for larger $\tau_0$.

%%TODO: Pick up here. Shane's edits, top of page 5
